Music Perception: Pilot Stimuli Analysis

### 2021-01-25 analysis/stimuli/stimuli_analysis.Rmd
add models
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r setup, include = FALSE}
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
```

@@

# IOIs
- average tempo and teaching judgement

@@

@@

## Dynamics
```{r ioi-all-dyn, echo = FALSE}
ioi_dyn <- dt_ioi[Skill == "dynamics", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile)]

@@

# Transition points
- tempo at transition points (e.g., legato to staccato / forte to piano) and teaching judgement

@@

@@

## Dynamics
```{r ioi-tra-dyn, echo = FALSE}
ioi_tra_dyn <- dt_ioi[Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile)]

@@

# CV (tempo variability)
- tempo variability and teaching judgement

@@

ggscatter(cv, x = "CV", y = "Teaching", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```
## Articulation
```{r cv-art, echo = FALSE}
cv_art <- dt_ioi[Skill == "articulation", .(N = .N, CV = sd(IOI)/mean(IOI)), by = .(MidFile)]

@@

@@

# KOT (only articulation stimuli)
- articulation and teaching judgement

@@

ggscatter(kot_legato, x = "Mean", y = "Teaching", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```
## Staccato
```{r kot-staccato, echo = FALSE}
kot_staccato <- dt_kot[Subcomponent == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile)]

@@

ggscatter(kot_staccato, x = "Mean", y = "Teaching", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```
# KV (only dynamics stimuli)
- dynamics and teaching judgement

@@

@@

# KV-diff (dynamics)
- dynamics changes at transition points (between forte and piano) and teaching judgement

@@

@@

>>>>

```{r setup, include = FALSE}
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("tuneR")) {install.packages("tuneR"); require("tuneR")}
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
if (!require("performance")) {install.packages("performance"); require("performance")}
```

@@

# IOIs
- average tempo and teaching judgement
- linear regression line (black) and 95% confidence interval (gray)

@@

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ Mean, data = ioi)
check_normality(model)
summary(model)
r2(model)
```

@@

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ Mean, data = ioi_art)
check_normality(model)
summary(model)
r2(model)
```
## Dynamics
```{r ioi-all-dyn, echo = FALSE}
ioi_dyn <- dt_ioi[Skill == "dynamics", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile)]

@@

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ Mean, data = ioi_dyn)
check_normality(model)
summary(model)
r2(model)
```

# Transition points
- tempo at transition points (e.g., legato to staccato / forte to piano) and teaching judgement
- linear regression line (black) and 95% confidence interval (gray)

@@

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ Mean, data = ioi_tra)
check_normality(model)
summary(model)
r2(model)
```

@@

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ Mean, data = ioi_tra_art)
check_normality(model)
summary(model)
r2(model)
```
## Dynamics
```{r ioi-tra-dyn, echo = FALSE}
ioi_tra_dyn <- dt_ioi[Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(MidFile)]

@@

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ Mean, data = ioi_tra_dyn)
check_normality(model)
summary(model)
r2(model)
```

# CV (tempo variability)
- tempo variability and teaching judgement
- linear regression line (black) and 95% confidence interval (gray)

@@

ggscatter(cv, x = "CV", y = "Teaching", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ CV, data = cv)
check_normality(model)
summary(model)
r2(model)
```

## Articulation
```{r cv-art, echo = FALSE}
cv_art <- dt_ioi[Skill == "articulation", .(N = .N, CV = sd(IOI)/mean(IOI)), by = .(MidFile)]

@@

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ CV, data = cv_art)
check_normality(model)
summary(model)
r2(model)
```

@@

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ CV, data = cv_dyn)
check_normality(model)
summary(model)
r2(model)
```

# KOT (only articulation stimuli)
- articulation and teaching judgement
- linear regression line (black) and 95% confidence interval (gray)

@@

ggscatter(kot_legato, x = "Mean", y = "Teaching", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ Mean, data = kot_legato)
check_normality(model)
summary(model)
r2(model)
```

## Staccato
```{r kot-staccato, echo = FALSE}
kot_staccato <- dt_kot[Subcomponent == "Staccato", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile)]

@@

ggscatter(kot_staccato, x = "Mean", y = "Teaching", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = TRUE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ Mean, data = kot_staccato)
check_normality(model)
summary(model)
r2(model)
```

# KV (only dynamics stimuli)
- dynamics and teaching judgement
- linear regression line (black) and 95% confidence interval (gray)

@@

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ Mean, data = vel_forte)
check_normality(model)
summary(model)
r2(model)
```

@@

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ Mean, data = vel_piano)
check_normality(model)
summary(model)
r2(model)
```

# KV-diff (dynamics)
- dynamics changes at transition points (between forte and piano) and teaching judgement
- linear regression line (black) and 95% confidence interval (gray)

@@

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ Mean, data = vel_diff_ftop)
check_normality(model)
summary(model)
r2(model)
```

@@

### Model
```{r, echo = FALSE}
model <- lm(Teaching ~ Mean, data = vel_diff_ptof)
check_normality(model)
summary(model)
r2(model)
```
